Effects of the body force on the evacuation dynamics

### 2020-01-09 paper.tex
algunas mejoras en la parte de bottleneck

Despite the presence of the FIS or FIF phenomenon, the evacuation time at a fixed value of $v_d$ decreases for increasing values of $k$. This means that stiffer pedestrians evacuate faster than soft pedestrians. In order to investigate this issue, we computed the mean velocity of the whole crowd as a function of the stiffens $k$. \textcolor{red}{agregar figura velocidad (k)}. \\

@@

The regime for $v_d<2\,$m/s can be... \textcolor{red}{completar}.\\

Besides, for a given $v_d$, the overlap increases as the $k$ value decreases. \textcolor{red}{Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals.} The increment in mean overlap, however, seems to be more significant than the mean degree. \\

>>>>

Despite the presence of the FIS or FIF phenomenon, the evacuation time at a fixed value of $v_d$ decreases for increasing values of $k$. This means that stiffer pedestrians evacuate faster than soft pedestrians. In order to investigate this issue, we computed the mean velocity of the whole crowd as a function of the stiffens $k$. Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the x-direction as a function of the stiffness $k$ for three different desired velocities. In all cases, the velocity increases with the stiffness. From $k_n=0$ to $k_n=$1.2~E4 the increment of velocity is not as significative as it is for higher $k_n$. \\

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_bottleneck.eps}\label{kn_vs_vx_bottleneck}}\\
\caption[width=0.47\columnwidth]{}
\end{figure}

@@

The regime for $v_d<2\,$m/s is different from the rest since most of the pedestrians are not touching each other. The only pedestrians who touch each other are the ones who are being re-injected in the room. The overlap is higher than, for example, $v_d=3\,$m/s because of the pedestrians who are re-injected bump against the bulk. \\

Besides, for a given $v_d$, the overlap increases as the $k$ value decreases. Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals ( this means more overlap between pedestrians). The increment in mean overlap, however, seems to be more significant than the mean degree. \\
